---
title: "Advanced Filters"
---

`ganalytics` provides functions that makes it easy to define filters using natural R language operators. This example shows how to use `ganalytics` to define dimension or metric filters that can be used by the `googleAnalyticsR` package. The current development version of `googleAnalyticsR` supports filters defined with `ganalytics`.

# Setup/Config

Note that this example requires the current development versions of the `googleAnalyticsR` (>=0.5.0.9000) and `ganalytics` (>=0.10.4.9000) R packages available from GitHub. To install these, run the following code in R:
```{r install, eval=FALSE}
devtools::install_github("MarkEdmondson1234/googleAnalyticsR")
devtools::install_github("jdeboer/ganalytics")
```

Once installed, load these packages. Please refer to the `googleAnalyticsR` package documentation on configuration steps you may need to complete in order to use the Google Analytics APIs.

```{r setup}
library(googleAnalyticsR)
library(ganalytics)
```

# Pull the Data

In this example, we'll define the following filters:
* Device category is desktop or tablet - a dimension filter using an OR condition.
* New visitors using either a desktop or tablet device - a dimension filter involving both an AND and an OR condition.
* At least one goal completion or transaction - a metric filter using an OR condition.

The above list of filters will be defined using `ganalytics` expressions as follows:

```{r define-filters}
# Device category is desktop or tablet - a dimension filter using an OR condition.
desktop_or_mobile <- Expr(~deviceCategory == "desktop") | Expr(~deviceCategory == "tablet")

# New visitors using either a desktop or tablet device - a dimension filter involving both an AND and an OR condition.
new_desktop_and_mobile_visitors <- Expr(~userType == "new") & desktop_or_mobile

# At least one goal completion or transaction - a metric filter using an OR condition.
at_least_one_conversion <- Expr(~goalCompletionsAll > 0) | Expr(~transactions > 0)
```

We can now use `googleAnalyticsR` to 

```{r pull-data, message=FALSE}
results <- google_analytics(
  viewId = view_id,
  date_range = c(start_date, end_date),
  metrics = c("users", "sessions", "goalCompletionsAll", "transactions"),
  dimensions = c("deviceCategory", "userType"),
  dim_filters = new_desktop_and_mobile_visitors,
  met_filters = at_least_one_conversion
)
```

```{r display-pulled-data}
kable(results)
```

